Sample-efficient Reinforcement Learning \\ with Implicitly Quantized Representations

### 2024-02-01 paper/main.tex
udpatedc
add reconstruction ablation
Start fig 1

\twocolumn[
% \icmltitle{Submission and Formatting Instructions for \\
%            International Conference on Machine Learning (ICML 2024)}
% \icmltitle{Sample-efficient Reinforcement Learning with Latent Representations}
\icmltitle{Sample-efficient Reinforcement Learning with Implicitly Quantized Representations}

@@

\begin{figure}[t!]
\centering\scriptsize
\resizebox{\columnwidth}{!}{%
\begin{tikzpicture}

@@

  % Lengths (this tunes distance)
  \newlength{\nodedist}\setlength{\nodedist}{2cm}

  % Styles (this tunes colours etc.)
  \tikzstyle{mynode}=[fill=blue!10!cyan,rounded corners=1pt,font=\tiny,inner sep=0]
  \tikzstyle{trap}=[mynode,trapezium,minimum width=1.5em, minimum height=2em,
                    trapezium left angle=-70, trapezium right angle=-70]
  \tikzstyle{blob}=[mynode,circle,minimum width=2.4em,minimum height=2.4em]
  \tikzstyle{polval}=[mynode,minimum width=6em,minimum height=2em,align=center,text=white,fill=black!60,inner sep=2pt]
  \tikzstyle{arr}=[line width=1pt,black,->]
  \tikzstyle{darr}=[line width=1pt,black,<->,densely dotted]

  % *** FIRST HALF ***

@@

  \node[trap] (e0) at (0\nodedist,\nodedist) {$e_\phi$};
  \node[trap] (e1) at (1\nodedist,\nodedist) {$e_{\bar\phi}$};
  \node[trap] (e2) at (2\nodedist,\nodedist) {$e_{\bar\phi}$};

@@

  \node[mynode,above of=e0] (i0) {\includegraphics[width=4.7em]{figs/humanoid-1}};
  \node[mynode,above of=e1] (i1) {\includegraphics[width=4.7em]{figs/humanoid-2}};
  \node[mynode,above of=e2] (i2) {\includegraphics[width=4.7em]{figs/humanoid-3}};

@@

  % *** SECOND HALF ***

  \node[blob] (z) at ($(e2) + (1.5\nodedist,0)$) {$\bar\vz_{\sub}$};
  \node[polval] (policy) at ($(z) + (-.5\nodedist,-.5\nodedist)$) {{\bf Policy} \\ $\pi_\theta(\va_t \mid \bar\vz_t)$};
  \node[polval] (value) at ($(z) + (.5\nodedist,-.5\nodedist)$) {{\bf Value} \\ $\mathcal{Q}_\psi(\bar\vz_t, \va_t)$};

  \draw[arr] (z) -- (policy);
  \draw[arr] (z) -- (value);

  \node[align=center] at ($(z)!(lab0)!(z)$) {\normalsize\bf 2.\ Latent actor-critic\vphantom{p}};

  % Draw backgrounds
  \begin{pgfonlayer}{background}

    \coordinate (mid) at ($(i2.east)!.5!(policy.west)$);

    \draw[draw=none,fill=black!10,rounded corners=5pt] ($(i0.north west) + (-.25cm,1cm)$) 
      rectangle ($(mid)!(z2.north)!(mid) + (-3pt,-1cm)$);

    \draw[draw=none,fill=black!05,rounded corners=5pt] ($(mid)!(i2.north east)!(mid) + (3pt,1cm)$) 
      rectangle ($(value.east)!(z2.north)!(value.east) + (.25cm,-1cm)$);

  \end{pgfonlayer}

\end{tikzpicture}}
%\centerline{\includegraphics[width=\columnwidth]{./figs/method-diagram.png}}
\caption{Self-predictice loss}
\label{diagram-self-predictive}
\vskip -0.2in
\end{figure}

>>>>

\twocolumn[
% \icmltitle{Submission and Formatting Instructions for \\
%            International Conference on Machine Learning (ICML 2024)}
% \icmltitle{Sample-efficient Reinforcement Learning with Latent Representations}
\icmltitle{Sample-efficient Reinforcement Learning \\ with Implicitly Quantized Representations}

@@

\begin{figure}[t!]
\centering\scriptsize
%\resizebox{\columnwidth}{!}{%
%\begin{tikzpicture}
%
%  % Declare that we have a background layer (advanced)
%  \pgfdeclarelayer{background}
%  \pgfsetlayers{background,main}
%
%  % Helpers for small subscripts
%  \newcommand{\sub}[0]{\scalebox{.8}{\ensuremath t}}
%  \newcommand{\subs}[1]{\scalebox{.8}{\ensuremath t{+}#1}}
%
%  % Lengths (this tunes distance)
%  \newlength{\nodedist}\setlength{\nodedist}{2cm}
%
%  % Styles (this tunes colours etc.)
%  \tikzstyle{mynode}=[fill=blue!10!cyan,rounded corners=1pt,font=\tiny,inner sep=0]
%  \tikzstyle{trap}=[mynode,trapezium,minimum width=1.5em, minimum height=2em,
%                    trapezium left angle=-70, trapezium right angle=-70]
%  \tikzstyle{blob}=[mynode,circle,minimum width=2.4em,minimum height=2.4em]
%  \tikzstyle{polval}=[mynode,minimum width=6em,minimum height=2em,align=center,text=white,fill=black!60,inner sep=2pt]
%  \tikzstyle{arr}=[line width=1pt,black,->]
%  \tikzstyle{darr}=[line width=1pt,black,<->,densely dotted]
%    
%  % *** FIRST HALF ***  
%    
%  % Draw nodes
%  \node[blob] (z0) at (0\nodedist,0) {$\vz_{\sub}$};
%  \node[blob] (z1) at (1\nodedist,0) {$\hat\vz_{\subs{1}}$};
%  \node[blob] (z2) at (2\nodedist,0) {$\hat\vz_{\subs{2}}$};
%
%  \node[trap] (e0) at (0\nodedist,\nodedist) {$e_\phi$};
%  \node[trap] (e1) at (1\nodedist,\nodedist) {$e_{\bar\phi}$};
%  \node[trap] (e2) at (2\nodedist,\nodedist) {$e_{\bar\phi}$};
%
%  \node[blob] (zh1) at ($(z1)!0.5!(e1)$) {$\bar\vz_{\subs{1}}$};
%  \node[blob] (zh2) at ($(z2)!0.5!(e2)$) {$\bar\vz_{\subs{2}}$};
%
%  \coordinate (m0) at ($(z0)!.5!(z1)$);
%  \node[blob] (a0) at ($(m0)!(zh1)!(m0)$) {$\va_{\sub}$};
%  \coordinate (m1) at ($(z1)!.5!(z2)$);
%  \node[blob] (a1) at ($(m1)!(zh2)!(m1)$) {$\va_{\subs{1}}$};
%  
%  \node[mynode,above of=e0] (i0) {\includegraphics[width=4.7em]{figs/bg}};
%  \node[mynode,above of=e1] (i1) {\includegraphics[width=4.7em]{figs/bg}};
%  \node[mynode,above of=e2] (i2) {\includegraphics[width=4.7em]{figs/bg}};
%  
%  \node[anchor=north] (o0) at (i0.north) {\color{white}$o_{\sub}$};
%  \node[anchor=north] (o1) at (i1.north) {\color{white}$o_{\subs{1}}$};
%  \node[anchor=north] (o2) at (i2.north) {\color{white}$o_{\subs{2}}$};
%  
%  \node[above of=i1,align=center] (lab0) {\normalsize\bf 1.\ Learn representation};
%    
%  % Draw arrows
%  \draw[arr] (i0) -- (e0);
%  \draw[arr] (i1) -- (e1);
%  \draw[arr] (i2) -- (e2);
%  \draw[arr] (z0) -- (z1);
%  \draw[arr] (z1) -- (z2);
%  \draw[arr] (e0) -- (z0);
%  \draw[arr] (e1) -- (zh1);
%  \draw[arr] (e2) -- (zh2);
%  \draw[arr] (a0) -- (z1);
%  \draw[arr] (a1) -- (z2);
%  \draw[darr] (zh1) -- (z1);
%  \draw[darr] (zh2) -- (z2); 
%  
%  
%  % *** SECOND HALF ***
%  
%  \node[blob] (z) at ($(e2) + (1.5\nodedist,0)$) {$\bar\vz_{\sub}$};
%  \node[polval] (policy) at ($(z) + (-.5\nodedist,-.5\nodedist)$) {{\bf Policy} \\ $\pi_\theta(\va_t \mid \bar\vz_t)$};
%  \node[polval] (value) at ($(z) + (.5\nodedist,-.5\nodedist)$) {{\bf Value} \\ $\mathcal{Q}_\psi(\bar\vz_t, \va_t)$};
%  
%  \draw[arr] (z) -- (policy);
%  \draw[arr] (z) -- (value);
%  
%  \node[align=center] at ($(z)!(lab0)!(z)$) {\normalsize\bf 2.\ Latent actor-critic\vphantom{p}};  
%
%  % Draw backgrounds
%  \begin{pgfonlayer}{background}
%  
%    \coordinate (mid) at ($(i2.east)!.5!(policy.west)$);  
%    
%    \draw[draw=none,fill=black!10,rounded corners=5pt] ($(i0.north west) + (-.25cm,1cm)$) 
%      rectangle ($(mid)!(z2.north)!(mid) + (-3pt,-1cm)$);
%      
%    \draw[draw=none,fill=black!05,rounded corners=5pt] ($(mid)!(i2.north east)!(mid) + (3pt,1cm)$) 
%      rectangle ($(value.east)!(z2.north)!(value.east) + (.25cm,-1cm)$);
%      
%  \end{pgfonlayer}
%  
%\end{tikzpicture}}

\begin{tikzpicture}

@@

  % Lengths (this tunes distance)
  \newlength{\nodedist}\setlength{\nodedist}{3cm}
  \newlength{\nodedistv}\setlength{\nodedistv}{2.5cm}

  % Styles (this tunes colours etc.)
  \tikzstyle{mynode}=[fill=white,draw=black!80,rounded corners=1pt,font=\tiny,inner sep=0]
  \tikzstyle{trap}=[mynode,trapezium,minimum width=1.5em, minimum height=2em,
                    trapezium left angle=-70, trapezium right angle=-70]
  \tikzstyle{blob}=[mynode,circle,minimum width=2.4em,minimum height=2.4em]
  \tikzstyle{polval}=[mynode,minimum width=6em,minimum height=2em,align=center,text=white,fill=black!60,inner sep=2pt]
  \tikzstyle{arr}=[line width=1pt,black,->]
  \tikzstyle{darr}=[line width=1pt,black,<->,densely dotted]

@@

  \node[trap] (e0) at (0\nodedist,\nodedistv) {$e_\phi$};
  \node[trap] (e1) at (1\nodedist,\nodedistv) {$e_{\bar\phi}$};
  \node[trap] (e2) at (2\nodedist,\nodedistv) {$e_{\bar\phi}$};

@@

  \node[mynode,above of=e0] (i0) {\includegraphics[width=4.7em]{figs/bg}};
  \node[mynode,above of=e1] (i1) {\includegraphics[width=4.7em]{figs/bg}};
  \node[mynode,above of=e2] (i2) {\includegraphics[width=4.7em]{figs/bg}};

@@

\end{tikzpicture}
\caption{Self-predictice loss}
\label{diagram-self-predictive}
\vskip -0.2in
\end{figure}
